---
title: "Shiny application presentation"
author: "Mahamane Sani Ibrahim"
date: "07/12/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
- The application allows to predict *child height* given his *gender* and parents *heights*
- We are using the *Galton Families* dataset to perform a linear regression.

## List of packages used to build thi app
- HistData
- GaltonFamilies
- dplyr
- ggplot2

```{r,echo=TRUE}
library(shiny)
library(HistData)
data(GaltonFamilies)
library(dplyr)
library(ggplot2)
```


## Data processing

- We convert inches to cm

```{r,echo=TRUE}
galtons<-GaltonFamilies
galtons$father<-galtons$father*2.54
galtons$mother<-galtons$mother*2.54
galtons$childHeight<-galtons$childHeight*2.54

```

## Exploratoring the dataset

```{r,echo=TRUE}
summary(galtons)
```

## Linear Model
- We perform a linear regression of the *childheight* against the independant variable *father height*, *mother height* and child *gender*

```{r,echo=TRUE}
fit<-lm(childHeight~father+mother+gender,data=galtons)
summary(fit)
```
